Robot Team III: Scotty Strikes Back

### 2024-04-30 paper/draft-introduction.tex

@@

>>>>

1. Remote sensing for water quality
2. Unsupervised approaches for remote sensing
3. UAV based Hyperspectral Imaging offers advantages for water composition analysis and characterization
4. Approaches for "Unsupervised" Analysis of 
    - Traditional Unsupervised Classification methods from ML
    - Endmember Extraction and Spectral Unmixing (i.e. assumption of linear mixing and projection-based and statistical methods for endmember extraction + abundance mapping)
5. Goal of this paper
    - The generative topographic mapping is an attractive algorithm 
        - Probabilistic interpretation
        - Topographic relationship maintained between classes (not just orthogonality)
        - clear fitting criterion with Maximum Likelihood Estimation / Maximum A-Posteriori Estimation
    - We use the GTM to analyze hyperspectral imagery acquired by a drone over pond to 
        - Present method for unsupervised characterization of small-scale variability of pond (i.e. identifying regions of interest which can be used to direct robot boat for further instructions) 
        - Use GTM to extract endmember for algae and map the algal distribution near shore (relevant for Harmful Algal Bloom detection)
        - Use GTM to extract endmember for rhodamine dye and use it to mape evolution of dye plume. This is a demonstration of source identification and mapping. Relevant for the identification of pollution events such as oil spills, industrial seepage, etc...

@@

The primary goal of this study...
